---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Sidney Hann"
date: "8/29/2019"
output: 
  html_document: 
    fig_height: 6
    fig_width: 8
    highlight: zenburn
    theme: sandstone
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

Datasaurus has 1846 rows and 3 columns.

### Exercise 2

Plot of the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Calculating the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

The data plot looks like a T-rex

### Exercise 3

Creating the plot for the star dataset

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculating the correlation between `x` and `y` in this dataset:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

The r value of this data set is very similar to the r value for dino. The coefficients are .015 away from each other and show almost zero correlation.

### Exercise 4

Creating the plot for the circle dataset

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculating the correlation between `x` and `y` in this dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

The r value of this data set is very similar to the r value for dino and star. The coefficients are all around -.06 and show almost no correlation.

### Exercise 5

Plotting all the datasets in the datasauRus library

```{r plot-all}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

Calculating the correlation between `x` and `y` in all datasets in the datasauRus library:

```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```